Plots_GAM

### 2024-05-21 Code/Plots_GAM.Rmd
Plos reveiwer Edits

# Set variables for project
```{r project data}
FP1 <- ".."
Project <- "PICO"
FileID <- "GAM"
Expert <- "MiSa" #MiSa SySl
GamFit <- "PICO_Merged_GrowthFitsPURPAR.Rds"

#"..", takes up a level in the directory path
DataIn <- file.path("..","Data", "CleanData")
DataOut <- file.path("..","Data", "CleanData")
PlotsOut <- file.path("..","Output", "Figures")
PlotsOutPLOS <- file.path("..", "OutPut", "PLOSFiguresRound1")

@@

GamPara <- "Lmu" # Stabds for growth estimates determined by logistic model

@@

```{r load libraries, message=FALSE}
library(tidyverse)
library(lubridate)
library(broom)
library(knitr)
library(minpack.lm)
library(nlstools)
library(nlsMicrobio)
library(plotly)
library(mgcv)
library(tidymv)
library(CCA)
library(vegan)
library(cowplot)
library(glue)
library(gtable)
library(car)
library(MASS) # estimating linear models through generalized least squares (GLS), fitting negative binomial linear models, the robust fitting of linear models, and Kruskal's non-metric multidimensional scaling.
library(faraway) # LM package
library(grid)
library(gridExtra)
library(ggh4x)
library(ggspectra) 
library(photobiologyWavebands) 
# library(photobiology)
library(metR)
library(Rcpp) #'Rcpp' package provides R functions as well as C++ classes which offer a seamless integration of R and C++.

@@

# Read data nad select relevant columns
```{r read data and select relevant columns}

@@

GrowthFits <- GrowthFits %>% 
 dplyr::select(c(Filename, PrimaryOperator, Tube, SampleID, Run, Photoperiod, Strain, WL, O2_Category, O2_uM, LightShape, Pur_ue, Par_ue, PURPhotonDose_day, PARPhotonDose_day, OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se))

ReplNo <- GrowthFits %>%
  distinct(Photoperiod, Strain, O2_uM, WL, Par_ue)

@@

# make df longer for GAM
```{r set up df for GAM}
 Pivot_Longer_OD720_est <- GrowthFits %>% 
  dplyr::select(-c(OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se)) %>%
   pivot_longer(c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')

# OD720 pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
Pivot_Longer_OD720_se <- GrowthFits %>%
  dplyr::select(-c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se)) %>%
   pivot_longer(c(OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')

@@

# deltaOD pivot longer Gmax, Gmu, Glag, Lmu, Lmax and Lintercept estimates
Pivot_Longer_deltaOD_est <- GrowthFits %>%
  dplyr::select(-c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se)) %>%
   pivot_longer(c(deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')

# deltaOD pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
Pivot_Longer_deltaOD_se <- GrowthFits %>%
  dplyr::select(-c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept)) %>%
   pivot_longer(c(deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')

@@

remove(Pivot_Longer_deltaOD_est, Pivot_Longer_deltaOD_se)

#Join OD720 and deltaOD fits data
ComGrowthFits <- rbind(Longer_OD720_Joined, Longer_deltaOD_Joined) %>%
  mutate_if(is.numeric, round, digits = 3) %>% 
  filter(Strain %in% c("MED4", "SS120", "MIT9313"),
         WL %in% c(450, 660, "WW"))

@@

glimpse(ComGrowthFits)

@@

```{r DF preparation Prochloroccus}
GamWL = "deltaOD"
GamVar = "450"

#DummyDF for MED4; MED4 is a high light strain, based on literature it can grow up to 800 uE; we never exposed it to such high light levels and will not impose an upper end, but only a lower, i.e. Par_ue = 0, Lmu = 0, there are no reliable points for low O2 in shorter photoperiods
Strain <- c("MED4")
Photoperiod <- c(4, 8, 12, 16)
Par_ue<- c(0)
O2_uM <- c(2.5, 25.0, 250.0)
WL <- c(450, 530, 660, "WW")
estimate <- c(0)
term <- GamPara
Wavelength <- c("deltaOD", "OD720")
Tube <- c(9)

DummyDF_MED4 <- expand_grid(
  Strain, Photoperiod, Par_ue, O2_uM, WL, estimate, Wavelength, term, Tube
  ) %>%
  mutate(Lmu_seFlag = 1) 
DummyDF_Expand_MED4 <- rbind(DummyDF_MED4, DummyDF_MED4, DummyDF_MED4)

#DummyDF for MIT9313; MIT9313 is a low light strain, based on literature it can only grow up to 300 uE WW; MIT9313 consistently died at various light colors and oxygen levels latest at ~PAR 400; it can safely be assumed it dies at par_ue = 0
Strain <- c("MIT9313")
Photoperiod <- c(4, 8, 12, 16)
Par_ue<- c(0)
O2_uM <- c(2.5, 25.0, 250.0)
WL <- c(450, 530, 660, "WW")
estimate <- c(0)
term <- GamPara
Wavelength <- c("deltaOD", "OD720")
Tube <- c(9)

DummyDF_MIT9313 <- expand_grid(
  Strain, Photoperiod, Par_ue, O2_uM, WL, estimate, Wavelength, term, Tube
  ) %>%
  mutate(Lmu_seFlag = 1) 
DummyDF_Expand_MIT9313 <- rbind(DummyDF_MIT9313, DummyDF_MIT9313, DummyDF_MIT9313)

#DummyDF for SS120; SS120 is a low light strain, based on literature it can only grow up to 300 uE WW; SS120 consistently died at various light colors and oxygen levels latest at ~PAR 400; it can safely be assumed it dies at par_ue = 0
Strain <- c("SS120")
Photoperiod <- c(4, 8, 12, 16)
Par_ue<- c(0, 400)
O2_uM <- c(2.5, 25.0, 250.0)
WL <- c(450, 530, 660, "WW")
estimate <- c(0)
term <- GamPara
Wavelength <- c("deltaOD", "OD720")
Tube <- c(9)

DummyDF_SS120 <- expand_grid(
  Strain, Photoperiod, Par_ue, O2_uM, WL, estimate, Wavelength, term, Tube
  ) %>%
  mutate(Lmu_seFlag = 1) 
DummyDF_Expand_SS120 <- rbind(DummyDF_SS120, DummyDF_SS120, DummyDF_SS120)

DummyDF_Expand <- rbind(DummyDF_Expand_SS120, DummyDF_Expand_MIT9313, DummyDF_Expand_MED4)

PicoGrowthFits <-    ComGrowthFits # full_join(ComGrowthFits, DummyDF_Expand)

PicoLmuAb <- PicoGrowthFits %>%
  filter(term %in% GamPara) %>%
  filter(Wavelength %in% GamWL) %>%
  filter(WL %in% GamVar) %>%
  mutate(Strain = as.factor(Strain))

@@

# Generate GAM for red light conditions for all strains using chlorophyll proxy logistic growth rate. 
```{r GAM separate niches hypervolume for red light}
GamWL = c("deltaOD", "OD720") #deltaOD OD720
Proxy= "[~Chl]" #~Chl ~Cells 
GamParaMod = "Lmu"
GamVar = c("660")
ErrorTolGrowth = 30 # defined for the growth estimates
ErrorTol = 30 # defined for the GAM fit
# OxyLev = 25

@@

PicoGAM_Pred <- PicoGAM %>%
  dplyr::select(Strain, Wavelength, WL, O2_uM, predicted) %>%
  dplyr::filter(predicted != "NULL") %>%
  rowwise() %>%
  mutate(db = list(cbind(predicted, PAR_Photoperiod_Model_predi))) %>%
  dplyr::select(-predicted) %>%
  unnest(col = db) %>%
  group_by(Strain, Wavelength, WL, O2_uM) %>%
  dplyr::filter(fit < 1.2) %>% #with two exceptions, growth rates were never higher than 1.2; GAM model creates some unrealistic high growth rates due to low data availability
  mutate(
    IsFitGood = case_when(se.fit/fit*100 < ErrorTol ~ 1, #flags faulty data where Standarderror larger +/- Errortolerance
                         se.fit/fit*100 > ErrorTol ~ 0
                    )
    #se_erro_per = se.fit/fit*100
  # ,fit = case_when(fit >= quantile(fit, 0.75, na.rm = TRUE) ~ fit*1, #leaves only top-10%, that means fastest growth rates in the dataframe
  #                 FALSE ~ fit)
  ) %>% 
  dplyr::filter(IsFitGood == 1)

# Generate GAM for blue light conditions for all strains using chlorophyll proxy logistic growth rate. 
```{r GAM separate niches hypervolume for blue light}
GamWL = c("deltaOD", "OD720") #deltaOD OD720
Proxy= "[~Chl]" #~Chl ~Cells 
GamParaMod = "Lmu"
GamVar = c("450")
ErrorTolGrowth = 30 # defined for the growth estimates
ErrorTol = 30 # defined for the GAM fit
# OxyLev = 25

PicoGAM_Pred <- PicoGAM %>%
  dplyr::select(Strain, Wavelength, WL, O2_uM, predicted) %>%
  dplyr::filter(predicted != "NULL") %>%
  rowwise() %>%
  mutate(db = list(cbind(predicted, PAR_Photoperiod_Model_predi))) %>%
  dplyr::select(-predicted) %>%
  unnest(col = db) %>%
  group_by(Strain, Wavelength, WL, O2_uM) %>%
  dplyr::filter(fit < 1.2) %>% #with two exceptions, growth rates were never higher than 1.2; GAM model creates some unrealistic high growth rates due to low data availability
  mutate(
    IsFitGood = case_when(se.fit/fit*100 < ErrorTol ~ 1, #flags faulty data where Standarderror larger +/- Errortolerance
                         se.fit/fit*100 > ErrorTol ~ 0
                    )
    #se_erro_per = se.fit/fit*100
  # ,fit = case_when(fit >= quantile(fit, 0.75, na.rm = TRUE) ~ fit*1, #leaves only top-10%, that means fastest growth rates in the dataframe
  #                 FALSE ~ fit)
  ) %>% 
  dplyr::filter(IsFitGood == 1)

@@

PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
  filter(Wavelength %in% PlotWL,
         Strain %in% GamStrain,
         WL %in% WL_nm) %>%
  mutate(
         OxygenLabel = "Oxygen concentration (uM)",
         O2_level = case_when(O2_uM == 2.5 ~ "low",
                              O2_uM == 25 ~ "intermediate",
                              O2_uM == 250 ~ "high"),
         Color_name = case_when(WL == "450" ~ 'Blue',
                                WL == "530" ~ 'Green',
                                WL == "660" ~ 'Red',
                                WL == "WW" ~ 'White')) %>%
  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)

@@

@@

@@

@@

```{r save MED4GAM plots}
# MED4GAM,png for manuscript
 ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)

# MED4GAM is Fig4.tiff for PLOSONE submission
 ggsave(file = file.path(PlotsOutPLOS, "Fig4.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")

>>>>

# Set variables for project
```{r project data}

GamFit <- "PICO_Merged_GrowthFitsPURPAR.Rds"

#"..", takes up a level in the directory path
DataIn <- file.path("..","Data", "CleanData")
DataOut <- file.path("..","Data", "CleanData")
PlotsIn <- file.path("..","Output", "Figures")
PlotsOut <- file.path("..","Output", "Figures")
PlotsOutPLOS <- file.path("..", "OutPut", "PLOSFiguresRound1")

@@

@@

```{r load libraries, message=FALSE}
library(tidyverse)
library(lubridate)
library(broom)
library(knitr)
library(minpack.lm)
library(nlstools)
library(nlsMicrobio)
library(plotly)
library(mgcv)
library(tidymv)
library(CCA)
library(vegan)
library(glue)
library(gtable)
library(car)
library(MASS) # estimating linear models through generalized least squares (GLS), fitting negative binomial linear models, the robust fitting of linear models, and Kruskal's non-metric multidimensional scaling.
library(faraway) # LM package
library(grid)
library(gridExtra)
library(ggh4x)
library(ggspectra) 
library(photobiologyWavebands) 
# library(photobiology)
library(metR)
library(Rcpp) #'Rcpp' package provides R functions as well as C++ classes which offer a seamless integration of R and C++.
library(patchwork)

@@

# Read data and select relevant columns
```{r read data and select relevant columns}

@@

GAMGrowthFits <- GrowthFits %>% 
 dplyr::select(c(Filename, PrimaryOperator, Tube, SampleID, Run, Photoperiod, Strain, WL, O2_Category, O2_uM, LightShape, Pur_ue, Par_ue, PURPhotonDose_day, PARPhotonDose_day, OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se))

@@

# make df longer for GAM
```{r set up df for GAM}
 Pivot_Longer_OD720_est <- GAMGrowthFits %>% 
  dplyr::select(-c(OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se)) %>%
   pivot_longer(c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')

# OD720 pivot longer  Lmu, Lmax and Lintercept standard error
Pivot_Longer_OD720_se <- GAMGrowthFits %>%
  dplyr::select(-c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se)) %>%
   pivot_longer(c(OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')

@@

# deltaOD pivot longer Lmu, Lmax and Lintercept estimates
Pivot_Longer_deltaOD_est <- GAMGrowthFits %>%
  dplyr::select(-c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se)) %>%
   pivot_longer(c(deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')

# deltaOD pivot longer Lmu, Lmax and Lintercept standard error
Pivot_Longer_deltaOD_se <- GAMGrowthFits %>%
  dplyr::select(-c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept)) %>%
   pivot_longer(c(deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')

@@

remove(Pivot_Longer_deltaOD_est, Pivot_Longer_deltaOD_se, GAMGrowthFits)

#Join OD720 and deltaOD fits data
PicoGrowthFits <- rbind(Longer_OD720_Joined, Longer_deltaOD_Joined) %>%
  mutate_if(is.numeric, round, digits = 3) %>% 
  filter(Strain %in% c("MED4", "SS120", "MIT9313"),
         WL %in% c(450, 660, "WW"))

@@

glimpse(PicoGrowthFits)

@@

```{r DF preparation Prochloroccus}
GamWL = "deltaOD"
GamVar = "450"
GAMParaMod = "Lmu" # Stands for growth estimates determined by logistic model

PicoLmuAb <- PicoGrowthFits %>%
  filter(term %in% GAMParaMod) %>%
  filter(Wavelength %in% GamWL) %>%
  filter(WL %in% GamVar) %>%
  mutate(Strain = as.factor(Strain))

@@

# Generate GAM for red light conditions for all strains using chlorophyll proxy logistic growth rate. 
```{r GAM separate niches hypervolume for red light}
GamWL = c("deltaOD") #deltaOD or OD720
GamParaMod = "Lmu" # logistic model growth estimates
GamVar = "660" # growth spectral wavelength
ErrorTolGrowth = 30 # the amplitude tolerance of the standard error of the fitted growth estimates
ErrorTol = 30 # the amplitude tolerance of the standard error of the fitted GAM

PicoGAM <- PicoGrowthFits %>%
  ungroup() %>%
  dplyr::mutate(Lmu_seFlag = case_when(se/estimate*100 < ErrorTolGrowth ~ 1, # flag to include data where Standarderror smaller than +/- Errortolerance
                         FALSE ~ 0)) %>%
  dplyr::filter(
                estimate == 0 |
                estimate != 0 & Lmu_seFlag == 1, # include no growths and growths that meet se tolerance. 
                term %in% GamParaMod, 
                Wavelength %in% GamWL
                ) %>%
  mutate(estimate = estimate*24, # to convert growth from per hour to per day
         se = se*24) %>% # to convert standard error from per hour to per day
  group_by(Strain, Wavelength, WL, O2_uM) %>%
  nest() %>%
  dplyr::arrange(Strain, Wavelength, WL, O2_uM) %>%
  mutate(GamModel = map(data, ~possibGAM(estimate ~ s(Par_ue, k = 3) + s(Photoperiod, k = 3) + ti(Photoperiod, Par_ue, k = 3),  data = .x,
                                    family = "gaussian"(link = "log"), 
                                    method = "REML")),
         predicted = map(GamModel, ~possibPRED(.x, newdata = PAR_Photoperiod_Model_predi, type = 'response', se.fit=TRUE)),
         augmented = map(GamModel, ~augment(.x))
         )

PicoGAM_Pred <- PicoGAM %>%
  dplyr::select(Strain, Wavelength, WL, O2_uM, predicted) %>%
  dplyr::filter(predicted != "NULL") %>%
  rowwise() %>%
  mutate(db = list(cbind(predicted, PAR_Photoperiod_Model_predi))) %>%
  dplyr::select(-predicted) %>%
  unnest(col = db) %>%
  group_by(Strain, Wavelength, WL, O2_uM) %>%
  dplyr::filter(fit < 1.2) %>% # with two exceptions, growth rates were never higher than 1.2; GAM model creates some unrealistic high growth rates due to low data availability
  mutate(
    IsFitGood = case_when(se.fit/fit*100 < ErrorTol ~ 1, # flags faulty data where Standarderror larger +/- Errortolerance
                         se.fit/fit*100 > ErrorTol ~ 0
                    )
  ) %>% 
  dplyr::filter(IsFitGood == 1)

# Generate GAM for blue light conditions for all strains using chlorophyll proxy logistic growth rate. 
```{r GAM separate niches hypervolume for blue light}
GamWL = c("deltaOD") #deltaOD or OD720
GamParaMod = "Lmu" # logistic model growth estimates
GamVar = "450" # growth spectral wavelength
ErrorTolGrowth = 30 # the amplitude tolerance of the standard error of the fitted growth estimates
ErrorTol = 30 # defined for the GAM fit

@@

PicoGAM_Pred <- PicoGAM %>%
  dplyr::select(Strain, Wavelength, WL, O2_uM, predicted) %>%
  dplyr::filter(predicted != "NULL") %>%
  rowwise() %>%
  mutate(db = list(cbind(predicted, PAR_Photoperiod_Model_predi))) %>%
  dplyr::select(-predicted) %>%
  unnest(col = db) %>%
  group_by(Strain, Wavelength, WL, O2_uM) %>%
  dplyr::filter(fit < 1.2) %>% #with two exceptions, growth rates were never higher than 1.2; GAM model creates some unrealistic high growth rates due to low data availability
  mutate(
    IsFitGood = case_when(se.fit/fit*100 < ErrorTol ~ 1, # flags faulty data where Standarderror larger +/- Errortolerance
                         se.fit/fit*100 > ErrorTol ~ 0
                    )
  ) %>% 
  dplyr::filter(IsFitGood == 1)

@@

PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
  filter(Wavelength %in% PlotWL,
         Strain %in% GamStrain,
         WL %in% WL_nm) %>%
  mutate(
         Color_name = case_when(WL == "450" ~ 'Blue',
                                WL == "530" ~ 'Green',
                                WL == "660" ~ 'Red',
                                WL == "WW" ~ 'White'))

@@

(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200))  +
    labs(title = bquote("D.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
    # xlab(NULL)+
    #   ylab(NULL)+ 
  theme_classic() +
   theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))

@@

(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
    # xlab(NULL) +
    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
theme_classic() +
   theme(axis.text=element_text(size=15),
         axis.title.x = element_blank(),
         axis.text.x = element_blank(),
          # axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))

@@

test <-  plot_grid(MED4PAR, LabelledCombinedGam, labels = "AUTO", ncol = 1) 
test
```

```{r, MED4PAR, fig.height=10, fig.width=10}
MyWavelengths = c("WW", 660, 450)

MCMIXColours = c("black", "brown", "steelblue")

names(MCMIXColours) <- MyWavelengths
MCMIXColours

  data_text <- data.frame( ParLabel=c("PAR~(µmol~photons~m^{-2}~s^{-1})"), OxygenLabel = c("Oxygen~concentration~(µM)"),Par_ue = c("30"), O2_uM = c("250"), label = c('A'))

MED4PAR <- GrowthFits %>%
   filter(Strain == "MED4",
           Par_ue %in% c(30,90,180),
          WL %in% c("WW", 450, 660),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~concentration~(µM)",
         WLlabelTitle = "Growth~wavelength~(nm)",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         # Par_ue = factor(Par_ue, levels = c(30, 90, 180)),
         # O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL = factor(WL, levels = c("WW", 660, 530, 450)),
         deltaOD_Lmu_corr_day = deltaOD_Lmu_corr * 24,
         deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24) %>% 
  ggplot()  +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
    geom_text(data=data_text, aes(x=5.5, y=0.8, label=label), size=7) +
 labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
  scale_y_continuous(breaks = c(0,0.25,  0.5, 0.75, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, factor(Par_ue, levels = c("30", "90","180"))), rows = vars(OxygenLabel, factor(O2_uM, levels= c("250", "25","2.5"))), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
     axis.title.x.bottom = element_text(size = 16, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 16, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 16, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 12, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 12, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
       strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 16),  #change legend title font size
        legend.text = element_text(size = 12),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth wavelength (nm)",
       fill = "Growth wavelength (nm)")
MED4PAR

@@

``` {r MED4GAM Plot Blue WL 250, fig.height=5, fig.width=5}
GamStrain = "MED4" 
GamColor = "Blue"
WL_nm = 450 
PlotWL <- "deltaOD"
data_text <- data.frame(label = c('450 nm, 250 µM'))
# data_textB <- data.frame(label = c('B'))

PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
  filter(Wavelength %in% PlotWL,
         Strain %in% GamStrain,
         WL %in% WL_nm) %>%
  mutate(
         Color_name = case_when(WL == "450" ~ 'Blue',
                                WL == "530" ~ 'Green',
                                WL == "660" ~ 'Red',
                                WL == "WW" ~ 'White'))

HyperChlPlot <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL,
         O2_uM == "250"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "250") 
ContourLines <- ContourLines$quantileValue

(ContourMED4BlueHigh <- ggplot(na.omit(HyperChlPlot)) + 
    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    geom_text(data=data_text, aes(x=6, y=180, label=label), size=4) +
     # geom_text(data=data_textB, aes(x=5, y=190, label=label), size=7) +
   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
    # xlab(NULL) +
    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
         axis.title.y = element_blank(),
         # axis.title.y = element_text(margin=margin(r=10)),
         axis.title.x = element_blank(),
        # axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.15,0.30),
        legend.text = element_text(size=11)))

```{r MED4GAM Plot Blue WL 250, fig.height=5, fig.width=5}
GamStrain = "MED4" 
GamColor = "Blue"
WL_nm = 450 
PlotWL <- "deltaOD"
data_text <- data.frame(label = c('450 nm, 25 µM'))

PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
  filter(Wavelength %in% PlotWL,
         Strain %in% GamStrain,
         WL %in% WL_nm) %>%
  mutate(
         Color_name = case_when(WL == "450" ~ 'Blue',
                                WL == "530" ~ 'Green',
                                WL == "660" ~ 'Red',
                                WL == "WW" ~ 'White'))

HyperChlPlot <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL,
         O2_uM == "25"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "25") 
ContourLines <- ContourLines$quantileValue

(ContourMED4BlueInt <- ggplot(na.omit(HyperChlPlot)) + 
    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    geom_text(data=data_text, aes(x=6, y=180, label=label), size=4) +
   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
    xlab("Photoperiod (h)") +
      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
    # xlab(NULL) +
    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
         # axis.title.y = element_text(margin=margin(r=10)),
         axis.title.y = element_blank(),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.15,0.30),
        legend.text = element_text(size=11)))

``` {r MED4GAM Plot Red WL 250, fig.height=5, fig.width=5}
GamStrain = "MED4" 
GamColor = "Red"
WL_nm = 660 
PlotWL <- "deltaOD"
data_textB <- data.frame(label = c('B'))
data_text <- data.frame(label = c('660 nm, 250 µM'))
